\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{soul}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{svg.path}


\definecolor{accentcolor}{HTML}{007000}
\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{cvgreen}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\definecolor{nice_blue}{RGB}{59,140,245}

\newcommand\boldblue[1]{\textcolor{nice_blue}{\textbf{#1}}}
\newcommand{\niceblue}[1]{\textcolor{nice_blue}{#1}}
\newcommand{\cvgreen}[1]{\textcolor{cvgreen}{#1}}
\newcommand{\accentcolor}[1]{\textcolor{accentcolor}{#1}}


% Adjust margins
\usepackage{geometry}
\geometry{left=1.25cm, top=1.5cm, right=1.25cm, bottom=1.5cm, footskip=-.5cm}

\urlstyle{same}

\raggedbottom
%\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{\vspace{-4pt}\raggedright\large\bfseries\color{black}}{}{0em}{}[{\color{black}\titlerule[1.5pt] \vspace{-5pt}}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\

    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    {\Huge \scshape Colin P. Roberts} \\ \vspace{1pt}
    Fort Collins, CO \\ \vspace{1pt}
    %\small \href{tel:+1-626-589-4001}{ \raisebox{-0.1\height}\faPhone\ \underline{+1-626-589-4001} ~}
    \href{mailto:robertsp@rams.colostate.edu}{\faEnvelope \ \accentcolor{robertsp@rams.colostate.edu}} ~
    \href{https://www.linkedin.com/in/colinproberts/}{\faLinkedin \ \accentcolor{ColinPRoberts}}  ~
    \href{https://github.com/ColinPR}{\faGithub \ \accentcolor{ColinPR}} ~
    \href{https://www.colinroberts.net}{\faGreaterThan \ \accentcolor{colinroberts.net}}
\end{center}

\vspace*{-10pt}
%------Professional Summary-------
\section{PROFESSIONAL SUMMARY}

    Mathematical physicist with a diverse background interested in developing novel computational methods for models that incorporate real world data. I am eager to explore new content and improve my technical skills and collaborative abilities in order to solve challenging problems. 
 \vspace{-5pt}
%-----------PROGRAMMING SKILLS-----------
\section{RELEVANT SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{

     \textbf{\normalsize{Applied math:}}{ \normalsize{Data assimilation, dimension reduction, principal component analysis, differential equations, tensor algebra, geometric algebra, discrete differential geometry, Gaussian mixture models, multiscale modeling}} \\
     \textbf{\normalsize{Communication:}}{ \normalsize{Teaching, delegation, research presentations, technical writing, remote collaboration}} \\
     \textbf{\normalsize{Programming and software:}}{ \normalsize{Python, Matlab, Java, Git, \LaTeX, Linux, SQL}} \\
     \textbf{\normalsize{Packages:}}{ \normalsize{Parallel computing toolbox, Numpy, Pandas, Matplotlib, TensorFlow}} \\	
	}}
 \end{itemize}
 \vspace{-25pt}

%-----------PROJECTS-----------
\section{RELEVANT EXPERIENCE}
   
\resumeSubHeadingListStart
          \resumeProjectHeading
          {\href{}{\textbf{\large{Graduate Student}}} $|$ \large{Collaboration, Research, and Teaching}}{08/2017 -- Present}
        %\vspace*{-1cm}
        \resumeProjectHeading{Colorado State University, Fort Collins, CO}{~}
          \resumeItemListStart
            \resumeItem{\normalsize{\textbf{Thesis:} Using Clifford Analysis to Study Inverse Tomography}}
            \resumeItem{Solo author of \normalsize{\emph{A Gelfand Transform for Spinor Fields on Embedded Riemannian Manifolds.} \href{https://arxiv.org/abs/2203.00118}{\accentcolor{[Preprint]}}}}
	\resumeItemListEnd

\resumeProjectHeading{\bf{Ongoing collaboration in Data Assimilation}}{~}
\resumeItemListStart
\resumeItem{\normalsize{Developing proprietary modular code base for projected particle filter algorithm. \href{https://github.com/ColinPR/projected_particle_filter.git}{\accentcolor{[Github]}}}}
\resumeItem{\normalsize{Optimizing algorithm performance through on-line dimension reduction while adding capability to probe for non-Gaussian behavior using time-varying Gaussian mixture models.}}
	\resumeItemListEnd
%\vspace*{-5pt}

%\vspace*{-5pt}
\resumeProjectHeading{\bf{Ongoing collaboration with NASA}}{~}
\resumeItemListStart
			\resumeItem{\normalsize{Collaborating with experts in electromagnetics and plasmas to continue work on the Maxwell--Vlasov equation.}}
	\resumeItemListEnd
\vspace*{-10pt}

\resumeProjectHeading{\bf{Teaching Background}}{~}
\resumeItemListStart
            \resumeItem{\normalsize{Taught 7 different courses over 10 semesters and developed the content of 4 courses.} \href{https://www.colinroberts.net/teaching.html}{\accentcolor{[Materials]}}}
            \resumeItem{\normalsize{Developed an open-source textbook and Matlab tools for an applied mathematics for chemists course. \href{https://github.com/ColinPR/mathematics_for_physicists_and_chemists.git}{\accentcolor{[Github]}}}}
          \resumeItemListEnd
\vspace*{-10pt}
       \resumeProjectHeading
          {\href{https://intern.nasa.gov/}{\textbf{\large{NASA: Internship Program} \small{\raisebox{-0.1\height}\faExternalLinkSquareAlt}}} $|$ \href{https://www.mathjobs.org/jobs/list/17245?rss}{\large{Topological Plasmas}}}{06/2021 -- 08/2021}
        %\vspace*{-1cm}
        \resumeProjectHeading{NASA Glenn Research Center, Cleveland, OH (Remote)}{~}
          \resumeItemListStart
            \resumeItem{\normalsize{Worked with collaborators to develop a geometric framework for the Maxwell-Vlasov equation for plasmas.}}
          \resumeItemListEnd
        % \vspace{-5pt}
      \resumeProjectHeading{\href{https://aimath.org/workshops/upcoming/mcrn2020/}{\textbf{\large{AIM: Summer Program on COVID-19 Modeling} \small{\raisebox{-0.1\height}\faExternalLinkSquareAlt}}} $|$ \href{https://mathcommunities.org/taking-aim-at-covid-19/}{\large{Multiscale Modeling}}}{06/2020 -- 07/2020}
        %\vspace*{-1cm}
        \resumeProjectHeading{American Institute of Mathematics, San Jose, CA (Remote)}{~}
          \resumeItemListStart
            \resumeItem{\normalsize{Developed a multiscale epidemic model that incorporated real world data to predict the spread of COVID-19 in communities with schools.}} 
			\resumeItem{\normalsize{Presented our group's work and interviewed with American Institute of Mathematics. \href{https://mathcommunities.org/taking-aim-at-covid-19/}{\accentcolor{[Link]}}}}
			\resumeItem{\normalsize{Provided our codebase and insight to JBS Foods in Greeley, CO.} \href{https://github.com/clairevalva/mcrn_multi_DA}{\accentcolor{[Github]}}}
          \resumeItemListEnd
         %\vspace{-5pt}

          \resumeProjectHeading
          {\href{https://aimath.org/workshops/upcoming/mcrn2019/}{\textbf{\large{AIM: Engagement Program with MCRN}} \href{https://www.sciencedirect.com/science/article/abs/pii/S0898122121002121}{\raisebox{-0.1\height}\faExternalLinkSquareAlt }} $|$ \large{Data Assimilation}}{07/2019 -- Present}
       % \vspace*{-1cm}
        \resumeProjectHeading{Raleigh, NC \& Remote}{~}
          \resumeItemListStart
            \resumeItem{\normalsize{Worked collaboratively to develop novel data assimilation software for high-dimensional nonlinear systems and presented this work at numerous conferences. \href{https://www.sciencedirect.com/science/article/abs/pii/S0898122121002121}{\accentcolor{[Publication]}}}}
          \resumeItemListEnd


    \resumeSubHeadingListEnd
\vspace{-12pt}

%

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Colorado State University, \textnormal{Fort Collins, CO, USA}}{08/2012 -- Present}
      {Doctor of Philosophy, Mathematics}{Expected June 2022}
    \vspace*{-.7cm}
    \resumeSubheading{~}{~}{Bachelor of Science, Honors Student in Mathematics \& Physics}{May 2017}
  \resumeSubHeadingListEnd

\section{HOBBIES}

	I am an avid hiker, trail runner, and mountain biker. I also aspire to be a better chef, baker, and equity trader.


%%-----------INVOLVEMENT---------------
%\section{EXTRACURRICULAR}
%    \resumeSubHeadingListStart
%        \resumeSubheading{Organization Name \href{Certificate Proof link}{\raisebox{-0.1\height}\faExternalLink } }{MM YYYY -- MM YYYY}{\underline{Role}}{Location}
%            \resumeItemListStart
%                \resumeItem{\normalsize{About the role \textbf{and responsibilities carried out.}}}
%                \resumeItem{\normalsize{Participation Certificate. \href{ParticipationCertificateLink.com}{\raisebox{-0.1\height}\faExternalLink }}}
%            \resumeItemListEnd
%    \resumeSubHeadingListEnd
% \vspace{-11pt}
%
% %-----------CERTIFICATIONS---------------
%\section{CERTIFICATIONS}
%
%$\sbullet[.75] \hspace{0.1cm}$ {\href{certificateLink.com}{ReactJS \& Redux - Udemy}} \hspace{1.6cm}
%$\sbullet[.75] \hspace{0.1cm}$ {\href{certificateLink.com}{Java}} \hspace{2.59cm}
%$\sbullet[.75] \hspace{0.2cm}${\href{certificateLink.com} {Command Line in Linux - Coursera}}\\
%
%$\sbullet[.75] \hspace{0.2cm}${\href{certificateLink.com}{Python for Data Science - XIE}} \hspace{1cm}
%$\sbullet[.75] \hspace{0.1cm}$ {\href{certificateLink.com}{SQL}} \hspace{2.6cm}
%$\sbullet[.75] \hspace{0.2cm}${\href{certificateLink.com}{Microsoft AI Classroom - Microsoft}} \\
%
%$\sbullet[.75] \hspace{0.2cm}${\href{certificateLink.com}{\textbf{5 Stars} in \textbf{C++} \& \textbf{SQL} \href{certificateLink.com}{\raisebox{-0.1\height}\faExternalLink }}}\hspace{1.45cm}
%$\sbullet[.75] \hspace{0.2cm}${\href{certificateLink.com}{MongoDB Basics}} \hspace{0.5cm}
%$\sbullet[.75] \hspace{0.2cm}${\href{certificateLink.com}{NodeJS with Express \& MongoDB - Udemy}} \\


\end{document}
            